Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-19 paper/paper.tex
texto de los sistemas

>>>>

How can see in the table \ref{} BERT and variants predominate as feature extractor although
some teams add clasic NLP featuures.
In contrast with previus years the join aproche is used by more than the half of system that present in the involve task
Como en años anteriores the subtask A is model as sequens labeling using some variant of BIO encoding. 
Likewise the subtask B is commonly model as pair wise classification.

Two approaches break this treads IXA and VICONTECH, The fisrt model the task B
also as sequence labeling reusing the same arquitecture that subtask A.
Th second present a arquitecture text to text that translate que raw sentence To
a semiestructured representation where are encode all the entities and their relations.
